Preregistration, design, IRB

### 2018-02-09 experiment.Rmd
Rearrange site structure

## Description

This survey was hosted on [Qualtrics](https://www.qualtrics.com) and participants were randomly sorted into one of eight variations (see [Design](design.html)).

@@

```{r calculate-payment}
hourly.wage <- 9
survey.length.minutes <- 5

payment <- survey.length.minutes * (hourly.wage / 60)
payment
```

## Survey experiment {.survey}

### Consent

***Q1.1***: You have been invited to participate in an academic research survey about international nongovernmental organizations. This study is being conducted by Suparna Chaudhry from Dartmouth College and Andrew Heiss from Duke University. The experiment should take about **5 minutes** to complete. You will be paid **$0.75** for your participation.

@@

If you have any questions at any time about the study or the procedures, you can contact Suparna Chaudhry (Suparna.Chaudhry@dartmouth.edu; Dickey Center for International Understanding, Hanover, NH 03755) or Andrew Heiss (andrew.heiss@duke.edu; Sanford School of Public Policy, Durham, NC 27712) at andrew.heiss@duke.edu. This research has been reviewed by the Committee for the Protection of Human Subjects at Dartmouth College (603-646-6842; cphs.tasks@dartmouth.edu) and the Human Subjects Committee at Duke University (919-684-3030; campusirb@duke.edu).

@@

### Crackdown and private giving

@@

***Q2.1***: The **International Rescue Committee** (IRC) focuses on {ISSUE AREA: humanitarian assistance for refugees | human rights for refugees} {MAIN MANIPULATION: and works in countries that have recently passed laws that harshly restrict nonprofit organizations}.

@@

*Q2.2*: How likely would you be to donate to IRC?

@@

*Q2.3*: If you had an extra $100, how much would you be willing to donate to IRC right now? (*Total must add to 100*)

@@

*Q2.4*: Why would you donate that amount?

@@

### Crackdown and corporate social responsibility (CSR)

![](img/google_irc_logo.png "Google and IRC logos"){.img-responsive .center}

***Q3.1***: In December 2016, Google held a Giving Weekend and raised $X and did YYY to support International Rescue Committee’s (IRC) efforts in {ISSUE AREA: providing humanitarian assistance for refugees | advocating human rights for refugees} {in countries where nonprofit organizations are harshly restricted}.

*Q3.2*: How favorable do you feel towards Google?

    - Extremely positive
    - Somewhat positive
    - Neither positive nor negative
    - Somewhat negative
    - Extremely negative

*Q3.3*: How generous do you feel Google is?

    - Extremely generous
    - Very generous
    - Moderately generous
    - Slightly generous
    - Not generous at all

*Q3.4*: Rate how strongly you feel Google is committed to philanthropy:

    - Extremely committed
    - Very committed
    - Moderately committed
    - Slightly committed
    - Not committed at all

*Q3.5*: Where would you most like to see Google donate its money?

    - Nonprofit organizations or foundations working mostly in California
    - Nonprofit organizations or foundations working throughout the United States
    - Nonprofit organizations or foundations working mostly in foreign countries

*Q3.6*: Why do you think Google should donate money to organizations working in X?

### Demographics

***Q4.1***: Almost done! This is the last page of the study.

*Q4.2*: How often do you donate to charity (either cash or in-kind)?

@@

*Q4.3*: Have you volunteered in the past 12 months?

@@

*Q4.4*: Some people seem to follow what's going on in government and public affairs most of the time, whether there's an election going on or not. Others aren't that interested. Would you say that you follow what's going on in government and public affairs…

@@

*Q4.5*: How would you describe your political views?

@@

*Q4.6*: What is the highest degree or level of school you have completed?

@@

*Q4.7*: Aside from weddings and funerals, how often do you attend religious services?

@@

*Q4.8*: Please select blue from the following list:

@@

*Q4.9*: What is your gender?

@@

*Q4.10*: What is your total household income?

@@

*Q4.11*: How old are you?

>>>>

# Description

This survey was hosted on [Qualtrics](https://www.qualtrics.com) and participants were randomly sorted into [one of eight conditions](preregistration.html#experimental_conditions).

@@

```{r calculate-payment}
hourly_wage <- 9
survey_length_minutes <- 5

payment <- survey_length_minutes * (hourly_wage / 60)
payment
```

# Survey experiment {.survey}

## Consent

***Q1.1***: You have been invited to participate in an academic research survey about international nongovernmental organizations. This study is being conducted by Suparna Chaudhry from Christopher Newport University and Andrew Heiss from Brigham Young University. The experiment should take about **5 minutes** to complete. You will be paid **$0.75** for your participation.

@@

If you have any questions at any time about the study or the procedures, you can contact Suparna Chaudhry (suparna.chaudhry@cnu.edu; Reiff Center for Human Rights and Conflict Resolution, Christopher Newport University, Newport News, VA 23606) or Andrew Heiss (andrew_heiss@byu.edu; Romney Institute of Public Management, Brigham Young University, Provo, UT 84602) at andrew_heiss@byu.edu. This research has been reviewed by the Institutional Review Board at Christopher Newport University (757-594-7461; IRB@cnu.edu) and the IRB administrator at Brigham Young University (801-422-1461; irb@byu.edu).

@@

## Crackdown and private giving

*Q2.1*: How do you feel about the following types of organizations?

:   Matrix table

    |                                                                          | Very unfavorable | Unfavorable | Neutral | Favorable | Very favorable |
    |--------------------------------------------------------------------------|:----------------:|:-----------:|:-------:|:---------:|:--------------:|
    | Nonprofit organizations that provide humanitarian relief                 |         ⊚        |      ⊚      |    ⊚    |     ⊚     |        ⊚       |
    | Nonprofit organizations that advocate for human rights                   |         ⊚        |      ⊚      |    ⊚    |     ⊚     |        ⊚       |
    | Nonprofit organizations that help with development and alleviate poverty |         ⊚        |      ⊚      |    ⊚    |     ⊚     |        ⊚       |

@@

*Q2.2*: The **International Rescue Committee** (IRC) focuses on {ISSUE AREA: humanitarian assistance for refugees | human rights for refugees} {MAIN MANIPULATION: and works in countries that have recently passed laws that harshly restrict nonprofit organizations}.

@@

*Q2.3*: How likely would you be to donate to IRC?

@@

*Q2.4*: If you had an extra $100, how much would you be willing to donate to IRC right now? (*Total must add to 100*)

@@

*Q2.5*: Why did you select that amount?

@@

## Demographics

*Q3.1*: Almost done! This is the last page of the study.

*Q3.2*: How often do you donate to charity (either cash or in-kind)?

@@

*Q3.3*: Have you volunteered in the past 12 months?

@@

*Q3.4*: Some people seem to follow what's going on in government and public affairs most of the time, whether there's an election going on or not. Others aren't that interested. Would you say that you follow what's going on in government and public affairs…

@@

*Q3.5*: How would you describe your political views?

@@

*Q3.6*: What is the highest degree or level of school you have completed?

@@

*Q3.7*: Aside from weddings and funerals, how often do you attend religious services?

@@

*Q3.8*: Please select blue from the following list:

@@

*Q3.9*: What is your gender?

@@

*Q3.10*: What is your total household income?

@@

*Q3.11*: How old are you?

### 2018-02-09 preregistration.Rmd
Rearrange site structure

---
title: "Preregistration & IRB"
date: "Last run: `r format(Sys.time(), '%F')`"
---

## Experiment preregistration

We have preregistered this study with the [Center for Open Science's](https://cos.io/) [Open Science Framework](https://osf.io/).

@@

We are also participating in COS's [Preregistration Challenge](https://cos.io/our-services/prereg-more-information/), and will submit our final article to one of the following eligible journals:

@@

## Human subjects and IRB approval

@@

### Project title

@@

### Purpose of the study

@@

### Participant activities

@@

### Subject selection and recruitment

@@

### Data security and participant privacy

@@

### Compensation

@@

Previous studies have found that including simple questions to screen for attention can improve the results of MTurk experiments and filter out workers who try to get through the HIT as quickly as possible without reading the questions.[^1] To ensure that participants only receive compensation for completing the full experiment, we include two attention check questions. The first (Q1.3) involves reading several sentences and following instructions to select specific responses. The second (Q4.8) is simpler and asks the respondent to select a single color from a list.

[^1]: Adam J. Berinsky, Michele F. Margolis, and Michael W. Sances, “Separating the Shirkers from the Workers? Making Sure Respondents Pay Attention on Self-Administered Surveys,” *American Journal of Political Science* 58, no. 3 (July 2014): 739–53. doi: [10.1111/ajps.12081](https://dx.doi.org/10.1111/ajps.12081)

@@

### Risks and benefits

@@

>>>>

---
title: "Preregistration, design, IRB"
date: "Last run: `r format(Sys.time(), '%F')`"
bibliography: manuscript/bibliography.bib
---

# Preregistration

We will preregister this study with the [Center for Open Science's](https://cos.io/) [Open Science Framework](https://osf.io/).

@@

We will also participate in COS's [Preregistration Challenge](https://cos.io/our-services/prereg-more-information/), and will submit our final article to one of the following eligible journals:

@@

# Design

## Experimental conditions

| Condition            | 1 | 2 | 3 | 4 | 5 | 6 | 7 | 8 |
|----------------------|:-:|:-:|:-:|:-:|:-:|:-:|:-:|:-:|
| **Crackdown**        |   |   |   |   |   |   |   |   |
| Yes                  | • | • | • | • |   |   |   |   |
| No                   |   |   |   |   | • | • | • | • |
| *Expected donations* | + | + | + | + | ∅ | ∅ | ∅ | ∅ |
|                      |   |   |   |   |   |   |   |   |
| **Issue area**       |   |   |   |   |   |   |   |   |
| Humanitarian service | • | • |   |   | • | • |   |   |
| Human rights         |   |   | • | • |   |   | • | • |
| *Expected donations* | + | + | − | − | + | + | − | − |
|                      |   |   |   |   |   |   |   |   |
| **Type of funding**  |   |   |   |   |   |   |   |   |
| Government           | • |   | • |   | • |   | • |   |
| Private              |   | • |   | • |   | • |   | • |
| *Expected donations* | − | + | − | + | − | + | − | + |

## $f^2$ power analysis

The ultimate goal of our research project is to use Bayesian analysis is to test if the region of practical equivalence around the null value (i.e. the proposition that the average treatment effect of NGO crackdown is zero) excludes the posterior 95% HDI.

In this initial pilot study, we use standard frequentist methods to perform power analysis and estimate the desired sample size. We will use the effect size estimates from this study to inform the prior distribution of parameter values in future Bayesian-based experiments [@Kruschke:2015, 362].

```{r power-calculations}
library(pwr)
u_mine <- 1
# f2_mine <- cohen.ES(test = "f2", size = "small")$effect.size
f2_mine <- 0.02
sig_level_mine <- 0.05
power_mine = 0.90

survey_power <- pwr.f2.test(u = u_mine, v = NULL, f2 = f2_mine, 
                            sig.level = sig_level_mine, power = power_mine)

# n = u + v + 1
n_total <- survey_power$u + survey_power$v + 1
n_group <- n_total / (2 * 2 * 2)
```

Cohen's rules of thumb for $f^2$ power are 0.02, 0.15, and 0.35 for small, medium, and large effect sizes.

We are using a 2 × 2 × 2 design, manipulating the experimental condition, the issue area for the NGO, and the source of funding for the NGO. The formula for calculating the $f^2$-based sample size with [`pwr.f2.test`](https://www.rdocumentation.org/packages/pwr/versions/1.2-0/topics/pwr.f2.test) requires the following values:

- `u`: degrees of freedom for the numerator. This is a 2 × 2 × 2 design, so the degrees of freedom = $(2 - 1) \times (2 - 1) \times (2 - 1) = 1$
- `f2`: effect size. Here we use a small size, or `r f2_mine`.
- `sig.level`: significance level, or Type I error probability. Here we use `r sig_level_mine`.
- `power`: power of test, or 1 − Type II error probability. Here we use `r power_mine`.

Given these parameters, `pwr.f2.test` yields `v`, or the degrees of freedom for the denominator. The final sample size `n` is calculated as `u + v + 1`.

Thus, the total sample size is **`r round(n_total, 2)`**, with **`r round(n_group, 2)`** spread across 8 groups.

# Human subjects and IRB approval

@@

## Project title

@@

## Purpose of the study

@@

## Participant activities

@@

## Subject selection and recruitment

@@

## Data security and participant privacy

@@

## Compensation

@@

Previous studies have found that including simple questions to screen for attention can improve the results of MTurk experiments and filter out workers who try to get through the HIT as quickly as possible without reading the questions [@BerinskyMargolisSances:2014]. To ensure that participants only receive compensation for completing the full experiment, we include two attention check questions. The first (Q1.3) involves reading several sentences and following instructions to select specific responses. The second (Q4.8) is simpler and asks the respondent to select a single color from a list.

@@

## Risks and benefits

@@

# References
